Reanalysis Step 2: Multiple Imputation

### 2025-08-26 reanalysis-2-multiple_imputation.qmd
2 - bug fix

# Show predictor matrix summary
# Calculate average predictors (excluding self-predictions)
avg_predictors <- round(mean(rowSums(pred_matrix[pred_matrix != 0, ])), 1)
predictors <- names(which(colSums(pred_matrix) > 0))

>>>>

# Show complete variables with methods assigned
complete_with_methods <- final_methods |>
  filter(N_Missing == 0 & Method != "") |>
  select(Variable, Type)
```

**Complete variables with imputation methods assigned** (`r nrow(complete_with_methods)` total):
These variables have no missing data and won't be imputed, but have methods specified to ensure proper measurement level:
```{r complete-vars-table}
if (nrow(complete_with_methods) > 0) {
  kable(complete_with_methods, col.names = c("Variable", "Method Type"))
} else {
  cat("No complete variables with methods assigned")
}

# Show predictor matrix summary
# Calculate average predictors (excluding self-predictions)
avg_predictors <- round(mean(rowSums(pred_matrix)), 1)
predictors <- names(which(colSums(pred_matrix) > 0))
